A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-21 camera-ready-paper/paper.tex
Added camera-ready source files

The algorithm builds up a mapping $M$ using a depth-first search, starting with the empty mapping
$\emptyset$ and adding a $(v_i, w_i)$ pair at each level of the search tree.
Select a vertex in $\V(\graphG)$ as the first vertex to be mapped; in our
example we will arbitrarily choose vertex $1$. Each of the vertices in
$\V(\graphH)$ to which vertex $1$ may be mapped will be tried in turn, and
finally the possibility where vertex $1$ remains unmatched will be tried.

>>>>

The algorithm builds up a mapping $M$ using a depth-first search, starting with the empty mapping
$\emptyset$ and adding a $(v_i, w_i)$ pair or choosing to leave a vertex in $\V(\graphG)$ unmatched at each level of the search tree.
Select a vertex in $\V(\graphG)$ as the first vertex to be mapped; in our
example we will arbitrarily choose vertex $1$. Each of the vertices in
$\V(\graphH)$ to which vertex $1$ may be mapped will be tried in turn, and
finally the possibility where vertex $1$ remains unmatched will be tried.
